HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
edits

For example, 
%consider the sentence $s=$``We're driving back on Friday'' and the German
%translation t=``Am Freitag fahren wir zur\"uck'' (lit. ``on Friday driving we back'').
%``driving back'' will be aligned to ``fahren ... zur\"uck'',
%and ``wir'' will be marked as intervening word. Another example
in \figref{fig:interface}, ``ongoing pregnancy'' is translated to
``Schwangerschaft ... laufenden'' (lit. ``pregnancy ... ongoing''). The interleaving 
German words shown in red should not occur there, and the annotator should take this
into account and mark this structural node as ``B'', bad.

>>>>

For example, 
%consider the sentence $s=$``We're driving back on Friday'' and the German
%translation t=``Am Freitag fahren wir zur\"uck'' (lit. ``on Friday driving we back'').
%``driving back'' will be aligned to ``fahren ... zur\"uck'',
%and ``wir'' will be marked as intervening word. Another example
in \figref{fig:interface}, ``ongoing pregnancy'' is translated to
``Schwangerschaft ... laufenden'' (lit. ``pregnancy ... ongoing''). This alone
seems acceptable but the interleaving words in red notify the annotator to check
the whole translation. The meaning of the expression is not preserved in the
translation
and the annotator should mark this structural node as ``B'', bad. 
%The interleaving 
%German words shown in red should not occur there, and the annotator should take this
%into account and mark this structural node as ``B'', bad.
